Bayesian neural networks for sparse coding

### 2018-10-23 icassp_2019/paper.tex
Update icassp_2019/paper.tex
minor

\address{$^{\star}$ Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield S1 3JD, UK (e-mail: dkuzin1@sheffield.ac.uk; l.s.mihaylova@sheffield.ac.uk).\\
  		    $^{\dagger}$ Department of Engineering Science, University of Oxford, Oxford OX1 2JD, UK (e-mail: olga.isupova@eng.ox.ac.uk)}

>>>>

\address{$^{\star}$ Department of Automatic Control and Systems Engineering,\\
University of Sheffield, Sheffield S1 3JD, UK\\
e-mail: dkuzin1@sheffield.ac.uk; l.s.mihaylova@sheffield.ac.uk.\\
$^{\dagger}$ Department of Engineering Science,\\
University of Oxford, Oxford OX1 2JD, UK\\
e-mail: olga.isupova@eng.ox.ac.uk}
